---
title: "Author Scientific Summaries Using Ready4showSynopsis"
output: 
  rmarkdown::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Author Scientific Summaries Using Ready4showSynopsis}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---
```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE}
library(ready4show)
```

## Motivation
Open science workflows should ideally span an unbroken chain between data-ingest to production of a scientific summary such as a manuscript. Such extensive workflows provide an explicit means of linking all content in a scientific summary with the analysis that it reports. 

## Implementation
`ready4show` includes a number of classes and methods that help integrate manuscript authoring into a reproducible workflow. 

### Create a synopsis of the manuscript to be authored
To start with we create `X`, an instance of `Ready4showSynopsis`, a ready4framework module (S4) class. We can use `X` to record metadata about the manuscript to be authored (including details about the study being summarised and the title and format of the intended output).

```{r}
X <- Ready4showSynopsis(background_1L_chr = "Our study is entirely fictional and is for illustrative purposes.",
                        coi_1L_chr = "None declared.",
                        conclusion_1L_chr = "If this study was real, the results would be interesting.",
                        digits_int = 3L,
                        ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
                        funding_1L_chr = "The study was funded by Generous Benefactor.",
                        interval_chr = "three months",
                        keywords_chr = c("this","is","a","replication","using","fake","data","do", "not","cite"),
                        outp_formats_chr = "PDF",
                        sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
                        title_1L_chr = "A hypothetical study using fake data for instructional purposes only")
```

### Add authorship details
Authorship details can be added to slots of `X` that contain `ready4show_authors` and `ready4show_instututes` ready4 framework sub-modules.

```{r}
procureSlot(X,"authors_r3") # Add Exhibit Method
```

```{r}
X <- renewSlot(X,
          "authors_r3",
          new_val_xx = "use_renew_mthd",
          first_nm_chr = "Alejandra",
          middle_nm_chr = "Rocio",
          last_nm_chr = "Scienceace",
          title_chr = "Dr",
          qualifications_chr = "MD, PhD",
          institute_chr = "Institute_A, Institute_B",
          sequence_int = 1,
          is_corresponding_lgl = T,
          email_chr = "fake_email@fake_institute.com") %>%
  renewSlot("authors_r3",
            new_val_xx = "use_renew_mthd",
            first_nm_chr = "Fionn",
            middle_nm_chr = "Seamus",
            last_nm_chr = "Researchchamp",
            title_chr = "Prof",
            qualifications_chr = "MSc, PhD",
            institute_chr = "Institute_C, Institute_B",
            sequence_int = 2,
            email_chr = "fake_email@unreal_institute.com") 

```

```{r}
X %>%
  procureSlot("authors_r3") # Add Exhibit Method
```

```{r}
X <- renewSlot(X,
          "institutes_r3",
          new_val_xx = "use_renew_mthd",
          short_name_chr = "Institute_A", 
          long_name_chr = "Awesome University, Shanghai") %>%
  renewSlot("institutes_r3",
            new_val_xx = "use_renew_mthd",
            short_name_chr = "Institute_B", 
            long_name_chr = "August Institution, London") %>%
  renewSlot("institutes_r3",
            new_val_xx = "use_renew_mthd",
            short_name_chr = "Institute_C", 
            long_name_chr = "Highly Ranked Uni, Montreal")
  
```

```{r}
X %>%
  procureSlot("institutes_r3") # Add Exhibit Method
```
### Add correspondences
Finally we can add a look-up table about any changes we wish to make from the analysis code of how names of variables / parameters are presented in the manuscript text.

```{r}
X <- renewSlot(X,
               "correspondences_r3",
               new_val_xx = "use_renew_mthd",
               old_nms_chr = c("PHQ9","GAD7"),
               new_nms_chr = c("PHQ-9",
                               "GAD-7"))
```

```{r}
X %>%
  procureSlot("correspondences_r3") # Add Exhibit Method
```
